---
title: "family_by_order"
output:
  md_document:
    variant: markdown_github
---

# Get Families by Order.


We want to create graphs of the number of records of each family into each order.

We have a file with all the records within the folder `db`, it's called `raw_data_from_linaria_corregida.csv`and also we have other file with the taxonomy within the folder `data`, called `taxonomy.csv`. 

These two archives share the same column, id_dicc_especies. First we join the taxonomy ranks with the records of all species. 

```{r}
#di <- '/Users/ajpelu/ownCloud/MS/MS_DP_DISPERSANTES/dp_dispersantes'

di <- '/Users/iecolab/Documents/Lola/dp_dispersantes'

taxonomy <- read.csv(file=paste(di,"/data/taxonomy.csv", sep=""), header=TRUE, sep=",")
raw_data <- read.csv(file=paste(di,"/db/raw_data_from_linaria_corregida.csv", sep=""), header=TRUE, sep=";")
id <- raw_data[,c('id','nombre_cientifico','id_dicc_especies')]

```

Join the records of the species with the taxonomy data. 

```{r}
library('plyr')
data <- join(id, taxonomy, by='id_dicc_especies')
```

Now, we have all the records with it's taxonomy ranks (`data`). We can get all the records of the Order that we want, we are interested in the order with the highest number of recods (28437), Passeriformes. Then, we save the output as `/data/passeriformes.csv`.

```{r}
passeri <- subset(data, order == "Passeriformes")
write.csv(passeri, file = paste(di,"/data/passeriformes.csv", sep=""), row.names=FALSE, quote= FALSE)
```

Finally, we aggregate each record by it's family. We get how many records we have of each family of Passeriformes. 

```{r}

families_passeri <- aggregate(passeri$id, by=list(passeri$family), length)
names(families_passeri) <- c('Families','records')
families_passeri$per <- round((families_passeri$records/sum(families_passeri$records)*100),2)

write.csv(families_passeri, file = paste(di,"/data/familes_passeri.csv", sep=""), row.names=FALSE, quote= FALSE)

families_passeri
```
