---
title: "Get_taxonomic_coverage ☺"
output:
  md_document:
    variant: markdown_github
---
# Get taxonomic coverage

Our aim is get the taxonomic coverage. First of all, we read our occurences file within all the records (27847), `ocurrences.csv`. This archive is located in the folder `data/dicc_dwc/`.

At the same time, we get the taxonomy coverage only of the order Passeriformes, because we will use only these data for our dp. We get the families and genus of Passeriformes. 

```{r}
library(dplyr) 
# Set wd 
machine <- 'ajpeluLap'

di <- paste('/Users/', machine, '/ownCloud/MS/MS_DP_DISPERSANTES/dp_dispersantes', sep='')

# di <- '/Users/iecolab/Documents/Lola/dp_dispersantes'

# We work with occurrences table 
df <- read.csv(file=paste(di,"/data/dicc_dwc/ocurrences.csv", sep=""), header=TRUE, sep=";")

# Read the archive of the species records
# registros <- read.csv(file=paste(di,"/db/raw_data_from_linaria_corregida.csv", sep=""), header=TRUE, sep=";")
# reg <- registros[,c('id','nombre_cientifico','id_dicc_especies')]


# Leo datos de cobertura taxonomica (incluir enlace)
# taxonomy <- read.csv(file=paste(di,"/data/taxonomy.csv", sep=""), header=TRUE, sep=",")

# Select only taxonomy info 
df_tax <- df %>% 
  select(order, family, genus, specificepithet) %>%
  mutate(scientific_name_noAutor = paste(genus, specificepithet, sep=' '))


```

For Passeriformes and data from 2008 we got the taxonomic coverage. We got the number of records of each taxonomy rank and the percentage to total records. Finally, we save the results as a `.csv` in the folder `/data/taxo_coverage_output`.

#### Faimlies 
```{r family2008}
# Family Coverage
fam_cov <- df_tax %>% 
  group_by(family) %>% 
  summarise(n_records=length(scientific_name_noAutor)) %>%
  mutate(per=(n_records/sum(n_records))*100)

write.csv(fam_cov, file = paste(di,"/data/taxo_coverage_output/fam_cov2008.csv", sep=""), row.names=FALSE, quote= FALSE)

# Check n total (27847)
sum(fam_cov$n_records)
```

#### Genus 

```{r genus2008}
# Genus Coverage
gen_cov <- df_tax %>% 
  group_by(genus) %>% 
  summarise(n_records=length(scientific_name_noAutor)) %>%
  mutate(per=(n_records/sum(n_records))*100)

write.csv(gen_cov, file = paste(di,"/data/taxo_coverage_output/gen_cov2008.csv", sep=""), row.names=FALSE, quote= FALSE)

# Check n total (27847)
sum(gen_cov$n_records)

gen_cov
```

#### Species Coverage
```{r sp2008}
# Sp Coverage
sp_cov <- df_tax %>% 
  group_by(scientific_name_noAutor) %>% 
  summarise(n_records=length(scientific_name_noAutor)) %>%
  mutate(per=(n_records/sum(n_records))*100)

write.csv(sp_cov, file = paste(di,"/data/taxo_coverage_output/sp_cov2008.csv", sep=""), row.names=FALSE, quote= FALSE)

# Check n total (27847)
sum(sp_cov$n_records)

sp_cov
```




```{r Old version}

# Our aim is get the taxonomic coverage. First of all, we read our file within all the records (30324), `raw_data_from_linaria_corregida.csv`. This archive is located in the folder `db`. Then, we select the 'id', 'nombre_cientifico' and 'id_dicc_especies' variables.
# 
# At the same time, we get the taxonomy coverage only of the order Passeriformes, because we will use only these data for our dp. We get the families and genus of Passeriformes. 


# # Join the records of the species with the taxonomy data. 
# 
# 
# library('plyr')
# df <- join(reg, taxonomy, by='id_dicc_especies')
# 
# 
# Get the taxonomic coverage. We get the number of records of each taxonomy rank and the percentage to total records. Finally, we save the results as a `.csv` in the folder `/data/taxo_coverage_output`.
# 
# 
# # Orden
# orden <- aggregate(df$id, by=list(df$order), length)
# names(orden) <- c('Order','records')
# 
# orden$per <- round((orden$records/sum(orden$records)*100),2)
# 
# #Test that we have 30324 records. 
# sum(orden$records)
#               
# write.csv(orden, file = paste(di,"/data/taxo_coverage_output/orden_cov.csv", sep=""), row.names=FALSE, quote= FALSE)
# 
# # Family
# family <- aggregate(df$id, by=list(df$family), length)
# names(family) <- c('Family','records')
# 
# family$per <- round((family$records/sum(family$records)*100),2)
# 
# #Test that we have 30324 records. 
# sum(family$records)
#               
# write.csv(family, file = paste(di,"/data/taxo_coverage_output/family_cov.csv", sep=""), row.names=FALSE, quote= FALSE)
# 
# 
# # Families of Passeriformes. 
# 
# #en df tenemos todos los registros. Queremos coger solo aquellos en los que el orden sea passeriformes. 
# dfpasser <- subset(df,order=="Passeriformes")
# familypasser <- aggregate(dfpasser$id, by=list(dfpasser$family), length)
# names(familypasser) <- c('Family','records')
# 
# familypasser$per <- round((familypasser$records/sum(familypasser$records)*100),2)
# 
# #Test that we have 28437 records. 
# sum(familypasser$records)
#               
# write.csv(familypasser, file = paste(di,"/data/taxo_coverage_output/passerfamily_cov.csv", sep=""), row.names=FALSE, quote= FALSE)
# 
# familypasser 
# 
# # Genus
# genus <- aggregate(df$id, by=list(df$genus), length)
# names(genus) <- c('Genus','records')
# 
# genus$per <- round((genus$records/sum(genus$records)*100),2)
# 
# #Test that we have 28437 records. 
# sum(genus$records)
#               
# write.csv(genus, file = paste(di,"/data/taxo_coverage_output/genus_cov.csv", sep=""), row.names=FALSE, quote= FALSE, sep="")
# 
# 
# # Genus of Passeriformes. 
# 
# genuspasser <- aggregate(dfpasser$id, by=list(dfpasser$genus), length)
# names(genuspasser) <- c('Genus','records')
# 
# genuspasser$per <- round((genuspasser$records/sum(genuspasser$records)*100),2)
# 
# #Test that we have 28437 records. 
# sum(genuspasser$records)
#               
# write.csv(family, file = paste(di,"/data/taxo_coverage_output/passergenus_cov.csv", sep=""), row.names=FALSE, quote= FALSE)
# 
# genuspasser 
```


