---
title: "Get_table_passer"
output:
  md_document:
    variant: markdown_github
---

We want to generate the table1passer with information about the next fields: nombre_cientifico, id_dicc_especies, Spanish Red List, IUCN Global, Birds Directive, Bern, Born, Authority, English name and Spanish name and save as `./tables/table1passer.md`

We have information of the species `./data/taxa_list_STATUS.csv`. We created this csv by hand. For the column "IUCN Red List Category (Spain)" with information of the 'Libro Rojo de Aves de Espa?a'. 

To know what species are Passeriformes, we need to add the 'order' column from `./data/taxonomy.csv`

We save this table as `/data/taxa_list_STATUS_passer.csv`. With the tables generator tool, we will create the `table1passer`.


```{r}
#di <- '/Users/ajpelu/ownCloud/MS/MS_DP_DISPERSANTES/dp_dispersantes'
di <- '/Users/iecolab/Documents/Lola/dp_dispersantes'

taxonomy <- read.csv(file=paste(di,"/data/taxonomy.csv", sep=""), header=TRUE, sep=",")

##Unimos a la tabla del Status de las especies, la columna orden
tax_status <- read.table(file=paste(di,"/data/taxa_list_STATUS.csv", sep=""), header=TRUE, sep=",")
order <- taxonomy[,c('order','id_dicc_especies')]
library('plyr')
status_passer <- join(tax_status, order, by='id_dicc_especies')

## Nos quedamos solo con las especies cuyo orden sea passeriformes.
status_passeri <- subset(status_passer,order=="Passeriformes")

#Ahora borramos la columna orden y IUCN.Global. 
status_passeri$order <- NULL
status_passeri$IUCN.Global <- NULL

##Guardamos esta tabla como `/data/taxa_list_STATUS_passer.csv`. Con este archivo, en el generador de tablas crearemos la tabla1passer. 

write.table(status_passeri, file = paste(di,"/data/taxa_list_STATUS_passer.csv", sep=""), row.names=FALSE, quote= FALSE, sep = ";")
```

Modifications: We have to do some changes to get the final table. 

1. We remove the id_dicc_especies column because it is not necessary in the final table.

2. We combine the scientific name with the authory. 

3. We have to change the name of the columns. We save this table as `./data/taxa_passer_modif.csv`

4. Add the column "IUCN Red List Category (Europe)". For this column we use information from " Appendix 1 of 'Red List status of all European bird species and their protection status under international legislation, conventions and agreements'. We add this column by hand and save the table as `./data/taxa_passer_modif2.csv`. 


```{r}
data <- read.csv(file=paste(di,"/data/taxa_list_STATUS_passer.csv", sep=""), header=TRUE, sep=";")

##1.Delete id_dicc_species, Spanish name and English name
data$id_dicc_especies <- NULL
data$Spanish.Name <- NULL
data$English.Name <- NULL
head(data)

##2.Combine names
install.packages('tidyr')
library('tidyr')
##La funci?n unite nos permite unir el contenido de dos columnas, separando con el car?cter que queramos y borrar las dos columnas antiguas. 
data<- unite(data, nombre_cientif, nombre_cientifico, Authority, sep=' ', remove=TRUE)

#3. Rename columns
names(data) <- c("Scientific name", "Spanish Red List", "Birds Directive", "Bern", "Bonn")

write.table(data, file = paste(di,"/data/taxa_passer_modif.csv", sep=""), row.names=FALSE, quote= FALSE, sep = ";")
```
