---
title: "Get_taxonomic_coverage"
output:
  md_document:
    variant: markdown_github
---
Our aim is get the taxonomic coverage. First of all, we read our file within all the records (30324), `raw_data_from_linaria_corregida.csv`. This archive is located in the folder `db`. Then, we select the 'id', 'nombre_cientifico' and 'id_dicc_especies' variables.

```{r}
#di <- '/Users/ajpelu/ownCloud/MS/MS_DP_DISPERSANTES/dp_dispersantes'

di <- '/Users/iecolab/Documents/Lola/dp_dispersantes'

# Read the archive of the species records
registros <- read.csv(file=paste(di,"/db/raw_data_from_linaria_corregida.csv", sep=""), header=TRUE, sep=";")
reg <- registros[,c('id','nombre_cientifico','id_dicc_especies')]

# Leo datos de cobertura taxonomica (incluir enlace)
taxonomy <- read.csv(file=paste(di,"/data/taxonomy.csv", sep=""), header=TRUE, sep=",")
```

Join the records of the species with the taxonomy data. 

```{r}
library('plyr')
df <- join(reg, taxonomy, by='id_dicc_especies')
```

Get the taxonomic coverage. We get the number of records of each taxonomy rank and the percentage to total records. Finally, we save the results as a .csv in the folder `/data/taxo_coverage_output`.

```{r}
# Orden
orden <- aggregate(df$id, by=list(df$order), length)
names(orden) <- c('Order','records')

orden$per <- round((orden$records/sum(orden$records)*100),2)

#Test that we have 30324 records. 
sum(orden$records)
              
write.csv(orden, file = paste(di,"/data/taxo_coverage_output/orden_cov.csv", sep=""), row.names=FALSE, quote= FALSE)

orden 
```

```{r}
# Family
family <- aggregate(df$id, by=list(df$family), length)
names(family) <- c('Family','records')

family$per <- round((family$records/sum(family$records)*100),2)

#Test that we have 30324 records. 
sum(family$records)
              
write.csv(family, file = paste(di,"/data/taxo_coverage_output/family_cov.csv", sep=""), row.names=FALSE, quote= FALSE)

family 
```

```{r}
# Genus
genus <- aggregate(df$id, by=list(df$genus), length)
names(genus) <- c('Genus','records')

genus$per <- round((genus$records/sum(genus$records)*100),2)

#Test that we have 30324 records. 
sum(genus$records)
              
write.csv(genus, file = paste(di,"/data/taxo_coverage_output/genus_cov.csv", sep=""), row.names=FALSE, quote= FALSE)

genus
```